### 2015-05-05 background.tex
small fix

\begin{lstlisting}[caption = Data races in the generic\_nvram char driver that \whoop found., label = fig:data_race_example]
static loff_t nvram_llseek(struct file *file,
    loff_t offset, int origin) {
  switch (origin) {
    case 0:
      break;
    case 1:
      offset += file->f_pos; // racy
      break;
    case 2:
      offset += nvram_len;
      break;
    default:
      offset = -1;
  }
  if (offset < 0)
    return -EINVAL;
  file->f_pos = offset; // racy
  return file->f_pos; // racy
}
\end{lstlisting}

>>>>

\begin{lstlisting}[caption = Data races in a Linux driver that we discovered using \whoop., label = fig:data_race_example]
static loff_t nvram_llseek(struct file *file,
    loff_t offset, int origin) {
  switch (origin) {
    case 0:
      break;
    case 1:
      offset += file->f_pos; // racy
      break;
    case 2:
      offset += nvram_len;
      break;
    default:
      offset = -1;
  }
  if (offset < 0)
    return -EINVAL;
  file->f_pos = offset; // racy
  return file->f_pos; // racy
}
\end{lstlisting}
